Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-09-20 doc/manuscript/manuscript.Rmd
fix spelling of Sajeewa's name :no_mouth:

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amadarasa
    email: bamadarasa2@unl.edu
    affiliation: 1
  - name: Rachana Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: Serena McCoy
    email: serena.mccoy@icloud.com
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
header-includes: >
  \usepackage{indentfirst}
bibliography: ssc_bibliography.bib
csl: apa.csl
output: 
  rticles::peerj_article:
    citation_package: none
    base_format: bookdown::pdf_document2 # for using \@ref()
---

@@

 - **Bimal Sajeewa Amadarasa** ...

>>>>

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amaradasa
    email: bamaradasa2@unl.edu
    affiliation: 1
  - name: Rachana Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: Serena McCoy
    email: serena.mccoy@icloud.com
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
header-includes: >
  \usepackage{indentfirst}
bibliography: ssc_bibliography.bib
csl: apa.csl
output: 
  rticles::peerj_article:
    citation_package: none
    base_format: bookdown::pdf_document2 # for using \@ref()
---

@@

 - **Bimal Sajeewa Amaradasa** ...
